Abstract Shape Specifications for Stencil Verification

### 2016-02-02 paper.tex
change to the spec grammar

\begin{align*}
spec ::= & \; S  \; \texttt{,} \; spec \, \mid \, \epsilon \\ \\
%
S ::= &  \; \texttt{forward} \; [\textit{ixs}] \; [\textit{depth}] \\
& \; \mid \texttt{backward} \; [\textit{ixs}] \; [\textit{depth}] \\
& \; \mid \texttt{centered} \; [\textit{ixs}] \; [\textit{depth}] \\
& \; \mid \texttt{unspecified} \; [\textit{ixs}]
\end{align*}

>>>>

\begin{align*}
spec ::= & \; S  \; \texttt{,} \; spec \, \mid \, S \\[0.5em]
%
S ::= &  \; \texttt{forward} \; \textit{depth} \; \textit{dims} \\
& \; \mid \texttt{backward} \; \textit{depth} \; \textit{dims} \\
& \; \mid \texttt{centered} \; \textit{depth} \; \textit{dims} \\
& \; \mid \texttt{unspecified} \; [\textit{dims}] \\
& \; \mid \texttt{unique} \; S \\[0.5em]
\textit{depth} ::= & \; \mathbb{N} \\
\textit{dims}  ::= & \; \textit{var} \; \texttt{,} \; \textit{dims} \,
                      \mid \, \textit{var}
\end{align*}
